The Design of Shallow State Blockchain

### 2020-05-15 abstract.tex
修正章節概述

\bigbreak
\noindent \textbf{關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構}{\, \makeatletter \@keywordszh \makeatother}
\end{abstractzh}

@@

\bigbreak
\noindent \textbf{Keywords:blockchain, stateless blockchain, cache, data structure}{\, \makeatletter \@keywordsen \makeatother}
\end{abstracten}

\begin{comment}
\category{I2.10}{Computing Methodologies}{Artificial Intelligence --
Vision and Scene Understanding} \category{H5.3}{Information
Systems}{Information Interfaces and Presentation (HCI) -- Web-based
Interaction.}

\terms{Design, Human factors, Performance.}

\keywords{Region of interest, Visual attention model, Web-based
games, Benchmarks.}
\end{comment}

>>>>

\bigbreak
\noindent
關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構
\end{abstractzh}

@@

\bigbreak
\noindent
Keywords: blockchain, stateless blockchain, cache, data structure
\end{abstracten}

% \begin{comment}
% \category{I2.10}{Computing Methodologies}{Artificial Intelligence --
% Vision and Scene Understanding} \category{H5.3}{Information
% Systems}{Information Interfaces and Presentation (HCI) -- Web-based
% Interaction.}

% \terms{Design, Human factors, Performance.}

% \keywords{Region of interest, Visual attention model, Web-based
% games, Benchmarks.}
% \end{comment}

### 2020-05-15 ctapc/paper.tex
修正章節概述

The remaining sections are arranged as follows. Section II narratives some related works, whereas section III describes the background of this paper and preliminary knowledge; section IV illuminates the design of stateless blockchain, including cache strategies and data structures used by cache; section V shows the design and results of experiment; section VI discusses future extensions to stateless blockchain, and concluding remarks are found in section VII.

>>>>

The remaining sections are arranged as follows.
section II illuminates the design of stateless blockchain,
including cache strategies and data structures
used by cache; Section III narratives some related works,
and concluding remarks are found in section IV.
